DraftOne

### 2016-06-13 DraftOne.Rmd
Finishing sim_data function

```{r}
sim_data <- function(n, rr, x_type = "binary", trend = "constant",
                     start.date = "2000-01-01", ...){

@@

        if(trend=="constant"){
          if(x_type == "binary"){
            x <- binary_exposure(n=n, ...)
          }
          else if(x_type == "continuous"){
            x <- continuous_exposure(n=n, ...)
          }
          exp_base_y <- constant_baseline(n=n, ...)
          df <- full_join(x, exp_base_y, by="date") %>% mutate(exp_y = 
                 exp(log(exp_base_y)+log(rr)*x))
          df$y <- sapply(df$exp_y, FUN = function(x) rpois(1,x))
        }
        else if(trend != "constant"){
          t <- calc_t(n=n, ...)
          if(x_type == "binary"){
            x <- season_binexp(n = n,...)
          }
          else if(x_type == "continuous"){
            x <- season_contexp(n = n, ...)
          }
          exp_base_y <- 
        }
  return(df)
}

#????

        } else if(x_type == "binary" & trend != "constant"){
                x <- season_binexp(n = n, ...)
                simdata <- data.frame(x, sim_binout(n=n, ...))
        } else if(x_type == "continuous" & trend != "constant"){
                x <- season_contexp(n = n, ...)
                simdata <- data.frame(x, sim_contout(n=n, ...))
        }
        return(df)

>>>>

```{r}
sim_data <- function(n, rr, lambda, x_type = "binary", trend = "constant",
                     start.date = "2000-01-01", ...){

@@

        if(trend=="constant"){
          if(x_type == "binary"){
            x <- binary_exposure(n=n, ...)
          }
          else if(x_type == "continuous"){
            x <- continuous_exposure(n=n, ...)
          }
          exp_base_y <- constant_baseline(n=n, lambda = lambda, start.date = start.date)
          df <- full_join(x, exp_base_y, by="date") %>% mutate(exp_y = 
                 exp(log(exp_base_y)+log(rr)*x))
          df$y <- sapply(df$exp_y, FUN = function(x) rpois(1,x))
        }

        else if(trend != "constant"){
          if(x_type == "binary"){
            x <- season_binexp(n = n, ...)
          }
          else if(x_type == "continuous"){
            x <- season_contexp(n = n, trend = trend, ...)
          }
          exp_base_y <- seasonal_baseline(n = n, lambda = lambda, start.date = start.date,
                                          trend = trend)
          df <- full_join(x, exp_base_y, by="date") %>% mutate(exp_y = 
                exp(log(exp_base_y)+log(rr)*x))
          df$y <- sapply(df$exp_y, FUN = function(x) rpois(1,x))
        }
  return(df)
}
